---
title: "MSBR_70340_FinalProject"
author: "Christopher Rovero"
date: "2026-02-13"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Step 1: Clear Old Data
```{r}
rm(list = ls())
gc()
cat("\014")  
sessionInfo()
```

Step 2: Load Required Packages
```{r}
library(igraph)
library(ggraph)
library(tidygraph)
library(tergm)
library(btergm)
library(ergm)
library(EpiModel) # for diffusion
library(netdiffuseR) # for diffusion
library(gplots)
library(ggplot2)
library(ggpubr)
library(parallel)
library(dplyr)
library(tidyr)
library(knitr)
library(intergraph)
```

Step 3: Upload NHL Fight Network Data and Drop NA's
```{r}
getwd()
nodes_read <- read.csv("C:/Users/crovero/Downloads/node_list_2_(2).csv")
summary(nodes_read)
edges_read <- read.csv("C:/Users/crovero/Downloads/fighters_edge_list.csv")
summary(edges_read)

edges = drop_na(edges_read,ego_id,alter_id)
summary(edges)

nodes = drop_na(nodes_read,ego_id)
nodes$age <- as.numeric(nodes$age)
nodes$weight <- as.numeric(nodes$weight)
summary(nodes)

```

Step 4: Create Undirected and Directed Network Objects
```{r}
net <- igraph::graph_from_data_frame(edges, directed = T, vertices = nodes)
un_net <- igraph::graph_from_data_frame(edges, directed = F, vertices = nodes)

#Checking for Simplicity and Directedness of Objects
is_simple(net)
is_directed(net)
is_simple(un_net)
is_directed(un_net)
```
Step 4. Check our Degree and Create SubGraphs for Different Network Analysis
```{r}

#Create SubGraph that Removes Isolates from Directed Network
deg <- degree(net, mode="all")
deg_no_iso <- induced_subgraph(net, vids=which(deg>0))
deg_grt4 <- induced_subgraph(net, vids=which(deg>50))
vcount(deg_grt4)
ecount(deg_grt4)
sum(deg==0) #2703 Non-Fighters in the NHL
vcount(deg_no_iso) #1869 Fighters in the NHL 
ecount(deg_no_iso) #11324 Ties In the Network Still Matches Length of Edges


#Create SubGraph that Removes Isolates from Undirected Network
deg_un <- degree(un_net, mode="all")
deg_un_no_iso <- induced_subgraph(un_net, vids=which(deg_un>0))
sum(deg_un==0)


#Create SubGraph of Directed Network that Removes Players with Less Than 10 Fights
deg_2 <- degree(net, mode="all")
deg_grt2 <- induced_subgraph(net, vids=which(deg_2>10))
sum(deg_2==0)#2704 Non-Fighters in the NHL
sum(deg_2==1) #483 Players with 1 Fight
sum(deg_2==2) #239 Players with 2 Fights
vcount(deg_grt2) #508 Players Remaining with More than 10 Fights
ecount(deg_grt2) #7808 Remaining Ties In the Network

#Create SubGraph that Removes Players with Less Than 10 Fights from Undirected Network
deg_grt2_un <-induced.subgraph(un_net,vids=which(deg_un>10))
vcount(deg_grt2_un)
ecount(deg_grt2_un)

#Create SubGraph That Removes Players with More than 20 Fights
deg_grt3_un <-induced.subgraph(un_net,vids=which(deg_un>20)) 
vcount(deg_grt3_un)#322 Players Remaining with More than 20 Fights
ecount(deg_grt3_un)#5972 Ties Remaining

#Create SubGraph That Removes Players with Players with More than 45 Fights
deg_grt4_un <-induced.subgraph(un_net,vids=which(deg_un>45)) 
vcount(deg_grt4_un)#110 Players Remaining with More than 45 Fights
ecount(deg_grt4_un)#2346 Ties Remaining


#In Degree for Directed Network
deg_in <- igraph::degree(net, mode = "in") #in degree
which.max(deg_in) #Jared Boll (ego_id 3518 has the most fights lost at 86)
max(deg_in)

#Out Degree for Directed Network
deg_out <- igraph::degree(net, mode = "out") #out degree
which.max(deg_out) #Chris Neil (ego_id 4429 has the most fights won at 103)
max(deg_out)


#Degree for UnDirected Network
deg_in_u <- igraph::degree(un_net, mode = "in") #in degree
deg_in_u
which.max(deg_in_u) #Chris Neil (ego_id 4429 has the most total fights at 173)
max(deg_in_u)

```

Step 4: Plot the NHL Fight Network Data
```{r}
ggraph(un_net, layout = "stress") + 
  geom_edge_link() + 
  geom_node_point() +
  ggnetwork::theme_blank() #Background to White
```

Step 5: Lets Try Messing With the Node Size - Degree -In
```{r}
#Use Directed Network Object to Do In-Degree Graph Based on Node Size (Bigger if Fighter Loses)
ggraph(deg_grt2, layout="kk") + 
  geom_edge_link0(color = "black", alpha = .2) +
  geom_node_point(fill = "#EFD9D3", color = "black", shape = 21, 
                  size = sqrt(igraph::degree(deg_grt2, mode = "in"))) +
  ggnetwork::theme_blank()
```

Step 6: Lets Try Messing With the Node Size - Degree - Out
```{r}
#Use Directed Network Object to Do In-Degree Graph Based on Node Size (Bigger if Fighter Wins)
ggraph(deg_grt2, layout="kk") + 
  geom_edge_link0(color = "black", alpha = .12) +
  geom_node_point(fill = "#EFD9D3", color = "black", shape = 21, 
                  size = sqrt(igraph::degree(deg_grt2, mode = "out"))) +
  ggnetwork::theme_blank()

```

Step 7. Combine Step 7 With Adding Edge Direction to Graph Based on Node Size
```{r}
#Create a Network Diagram of Most Prevalent NHL Fighters by Total Altercation Count for Top 110 Fighters by Win
ggraph(deg_grt4_un, layout = "stress") + 
  geom_edge_link(aes(edge_colour= fight_relationship),
                                          alpha = .2,
                                          width = 1,
                 start_cap = circle(.9, 'mm'),
                 end_cap = circle(1.9, 'mm')) +
  scale_edge_colour_manual(values=c(
    "Interdivision" = "#82260d",
    "Interconference" = "steelblue",
    "Out-of-Conference" = "black"
  )) +
  geom_node_point(fill = "#EFD9D3", color = "black", shape = 21, 
                  aes(size = (igraph::degree(deg_grt4_un, mode = "out")))) +
                  labs(
                    title = "Network Diagram of Most Prevalant NHL Fighters by Total Altercation Count",
                    size = "Total Degree"
                  )+
                  theme(
                    plot.title = element_text(face = "bold", size = 14, hjust = 0.5),
                    plot.background = element_rect(fill = "white", color = NA),
                    legend.position = "bottom",
                    plot.margin = margin(10,40,10,10)) +
  ggnetwork::theme_blank()

#Create a Network Diagram of Most Prevalent NHL Fighters by Total Altercation Count for Top  by Win
ggraph(deg_grt2_un, layout = "stress") + 
  geom_edge_link(aes(edge_colour= fight_relationship),
                                          alpha = .2,
                                          width = 1,
                 start_cap = circle(.9, 'mm'),
                 end_cap = circle(1.9, 'mm')) +
  scale_edge_colour_manual(values=c(
    "Interdivision" = "#82260d",
    "Interconference" = "steelblue",
    "Out-of-Conference" = "black"
  )) +
  geom_node_point(fill = "#EFD9D3", color = "black", shape = 21, 
                  aes(size = (igraph::degree(deg_grt2_un, mode = "out")))) +
                  labs(
                    title = "Network Diagram of Experienced NHL Fighters by Total Altercation Count",
                    size = "Total Degree",
                    edge_colour = "Fight Relationship"
                    
                  )+
                  theme(
                    plot.title = element_text(face = "bold", size = 14, hjust = 0.5),
                    plot.background = element_rect(fill = "white", color = NA),
                    legend.position = "bottom",
                    plot.margin = margin(10,40,10,10)) +
  ggnetwork::theme_blank()

#Network Diagram of No Isolate Network
ggraph(deg_un_no_iso, layout = "stress") + 
  geom_edge_link(aes(edge_colour= fight_relationship),
                                          alpha = .2,
                                          width = 1,
                 start_cap = circle(.9, 'mm'),
                 end_cap = circle(1.9, 'mm')) +
  scale_edge_colour_manual(values=c(
    "Interdivision" = "#82260d",
    "Interconference" = "steelblue",
    "Out-of-Conference" = "black"
  )) +
  geom_node_point(fill = "#EFD9D3", color = "black", shape = 21, 
                  aes(size = (igraph::degree(deg_un_no_iso, mode = "all")))) +
                  labs(
                    title = "Network Diagram of NHL Fighters Players by Total Altercation Count",
                    size = "Total Degree",
                    edge_colour = "Fight Relationship"
                    
                  )+
                  theme(
                    plot.title = element_text(face = "bold", size = 14, hjust = 0.5),
                    plot.background = element_rect(fill = "white", color = NA),
                    legend.position = "bottom",
                    plot.margin = margin(10,40,10,10)) +
  ggnetwork::theme_blank()

#Network Diagram of Top 100 Fighters by Total Altercation Count
ggraph(deg_grt4_un, layout = "stress") + 
  geom_edge_link(aes(edge_colour= fight_relationship),
                                          alpha = .2,
                                          width = 1,
                 start_cap = circle(.9, 'mm'),
                 end_cap = circle(1.9, 'mm')) +
  scale_edge_colour_manual(values=c(
    "Interdivision" = "#82260d",
    "Interconference" = "steelblue",
    "Out-of-Conference" = "black"
  )) +
  geom_node_point(fill = "#EFD9D3", color = "black", shape = 21, 
                  aes(size = (igraph::degree(deg_grt4_un, mode = "out")))) +
                  labs(
                    title = "Network Diagram of Top 110 NHL Fighters Players by Total Altercation Count",
                    size = "Total Degree",
                    edge_colour = "Fight Relationship"
                    
                  )+
                  theme(
                    plot.title = element_text(face = "bold", size = 14, hjust = 0.5),
                    plot.background = element_rect(fill = "white", color = NA),
                    legend.position = "bottom",
                    plot.margin = margin(10,40,10,10)) +
  ggnetwork::theme_blank()

#Network Diagram of Top 100 Fighters by Total Altercation Count
ggraph(deg_grt4, layout = "stress") + 
  geom_edge_link(aes(edge_colour= fight_relationship),
                                          alpha = .3,
                                          width = 1,
                 arrow = arrow(type = "closed",length=unit(2,"mm")),
                 start_cap = circle(.5, 'mm'),
                 end_cap = circle(0.8, 'mm')) +
  scale_edge_colour_manual(values=c(
    "Interdivision" = "#82260d",
    "Interconference" = "steelblue",
    "Out-of-Conference" = "black"
  )) +
  geom_node_point(fill = "#EFD9D3", color = "black", shape = 21, 
                  aes(size = (igraph::degree(deg_grt4, mode = "all")))) +
                  labs(
                    title = "Network Diagram of Top 100 NHL Fighters Players by Total Altercation Count",
                    size = "Total Degree",
                    edge_colour = "Fight Relationship"
                    
                  )+
                  theme(
                    plot.title = element_text(face = "bold", size = 14, hjust = 0.5),
                    plot.background = element_rect(fill = "white", color = NA),
                    legend.position = "bottom",
                    plot.margin = margin(10,40,10,10)) +
  ggnetwork::theme_blank()

#Plotting Top 110 Fighters by Betweeness
ggraph(deg_grt2, layout = "stress") + 
  geom_edge_link(aes(edge_colour= fight_relationship),
                                          alpha = .3,
                                          width = 1,
                 arrow = arrow(type = "closed",length=unit(2,"mm")),
                 start_cap = circle(.5, 'mm'),
                 end_cap = circle(0.8, 'mm')) +
  scale_edge_colour_manual(values=c(
    "Interdivision" = "#82260d",
    "Interconference" = "steelblue",
    "Out-of-Conference" = "black"
  )) +
  geom_node_point(fill = "#EFD9D3", color = "black", shape = 21, 
                  aes(size = (igraph::betweenness(deg_grt2)))) +
                  labs(
                    title = "Network Diagram of Top 100 NHL Fighters Players by Betweeness",
                    size = "Betweeness",
                    edge_colour = "Fight Relationship"
                    
                  )+
                  theme(
                    plot.title = element_text(face = "bold", size = 14, hjust = 0.5),
                    plot.background = element_rect(fill = "white", color = NA),
                    legend.position = "bottom",
                    plot.margin = margin(10,40,10,10)) +
  ggnetwork::theme_blank()


```

Step 8. Verification Checks on Our Data to Understand Changing Edge Types
```{r}
players_season_division <- edges %>%
  transmute(
    missing_season,
    ego_id,  ego_division,
    alter_id, alter_division
  ) %>%
  pivot_longer(
    cols = c(ego_id, alter_id, ego_division, alter_division),
    names_to = c("side", ".value"),
    names_pattern = "(ego|alter)_(id|division)"
  ) %>%
  rename(player_id = id, division = division) %>%
  distinct(player_id, missing_season, division)

multi_division_players <- players_season_division %>%
  group_by(player_id, missing_season) %>%
  summarise(n_divisions = n_distinct(division), .groups = "drop") %>%
  filter(n_divisions > 1)

nrow(multi_division_players)                 
n_distinct(multi_division_players$player_id) 

multi_division_players %>% count(n_divisions) %>% arrange(n_divisions)

mobility_lookup <- multi_division_players %>%
  select(player_id, missing_season) %>%
  distinct()

edges_flagged <- edges %>%
  mutate(
    ego_mobile = paste(ego_id, missing_season) %in%
                 paste(mobility_lookup$player_id,
                       mobility_lookup$missing_season),
    alter_mobile = paste(alter_id, missing_season) %in%
                   paste(mobility_lookup$player_id,
                         mobility_lookup$missing_season)
  ) %>%
  mutate(mobility_edge = ego_mobile | alter_mobile)

sum(edges_flagged$mobility_edge)
mean(edges_flagged$mobility_edge)


#Testing Some Accuracy
deg_un_net_tbl <-as_tbl_graph(un_net)
deg_un_no_iso_tbl <- as_tbl_graph(deg_un_no_iso)
deg_grt2_tbl <- as_tbl_graph(deg_grt2_un)
deg_grt3_tbl <- as_tbl_graph(deg_grt3_un)
deg_grt4_tbl <- as_tbl_graph(deg_grt4_un)


deg_un_net_tbl %>%
  activate(edges) %>%
  as_tibble() %>%
  count(fight_relationship, sort = TRUE)


deg_un_no_iso_tbl %>%
  activate(edges) %>%
  as_tibble() %>%
  count(fight_relationship, sort = TRUE)

deg_grt2_tbl %>%
  activate(edges) %>%
  as_tibble() %>%
  count(fight_relationship, sort = TRUE)

deg_grt3_tbl %>%
  activate(edges) %>%
  as_tibble() %>%
  count(fight_relationship, sort = TRUE)

deg_grt4_tbl %>%
  activate(edges) %>%
  as_tibble() %>%
  count(fight_relationship, sort = TRUE)
```

Step 9. Plot EigenVector Centrality
```{r}
evc_undir <- eigen_centrality(deg_grt2_un, directed = F)$vector #must pull the vector
summary(evc_undir)

top_idx <-order(evc_undir,decreasing = TRUE)

ggraph(deg_grt2) + 
  geom_edge_link(aes(edge_colour= fight_relationship), alpha = .2, width = 0.1) +
  scale_edge_colour_manual(values=c(
    "Interdivision" = "#82260d",
    "Interconference" = "steelblue",
    "Out-of-Conference" = "black"
  )) +
  geom_node_point(fill = "#EFD9D3", color = "black", shape = 21, 
                  size = igraph::eigen_centrality(deg_grt2)$vector*15) +
                  labs(
                  title = "Network Diagram of Highest Eigenvector Centrality NHL Fighters",
                  size = "Eigenvector Centraility"
                  ) +
                  theme(
                    plot.title = element_text(face = "bold", size = 16, hjust = 0.5),
                    plot.background = element_rect(fill = "white", color = NA),
                    legend.position = "bottom",
                    plot.margin = margin(10,40,10,10),
                    panel.background = element_rect("white", color = NA),
                    legend.background = element_rect("white", color = NA))


vcount(deg_grt2)
range(V(deg_grt2)$ego_id)

```


Step 10. Lets Calculate Centralizations
```{r}
#Degree Centralization on No Isolates
cent_deg <- centr_degree(deg_un_no_iso, mode = "all")$centralization
round(cent_deg, digits = 2) #For our Network with No Isolates, We Have A Degree Centralization of 0.04. Extremely low and decentralized. Alot of players have a handful of fights  

#Degree Centralization on Players with Greater than 10 Fights
cent_deg2 <- centr_degree(deg_grt2_un, mode = "all")$centralization
round(cent_deg2, digits = 2) #For our Network with Fights Greater than 10 with Have Degree Centralization of 0.13. Recognizable core group of fighters but still not fairly high with one player dominating all fighting

#Degree Centralization on the Entire NHL Network
cent_all <- centr_degree(un_net, mode = "all")$centralization
round(cent_all, digits = 2) 
```

```{r}
#Closeness Centralization
#Closeness Centralization on No Isolates
cent_clo <- centr_clo(deg_un_no_iso, normalized=TRUE)$centralization
round(cent_clo, digits = 2) #Network with no isolates have closeness centralization of 1.43 (NaN)

#Closeness Centralization on Players with Greater than 10 Fights
cent_clo2 <- centr_clo(deg_grt2_un, mode = "all")$centralization
round(cent_clo2, digits = 2) #Network with greater than 10 fights has closeness centralization of 0.26

#Closeness Centralization on All NHL Network
cent_all4 <- centr_clo(un_net, mode = "all")$centralization
round(cent_all4, digits = 2)
```

```{r}
#Betweeness Centralization
cent_bet <- centr_betw(deg_un_no_iso)$centralization #No Isolates Network Has Between of 0.03
round(cent_bet, digits = 2)

cent_bet2 <- centr_betw(deg_grt2_un)$centralization #Betweeness Centralization of 0.06, there has been plenty of enforcers connecting across divisions, conferences, and eras
round(cent_bet2, digits = 2)

cent_all2 <- centr_betw(un_net)$centralization
round(cent_all2, digits = 2)
```

```{r}
#Eigenvector Centralization for No Isolates
cent_evc <- centr_eigen(deg_un_no_iso)$centralization #EigenVector Centralization of 0.97
round(cent_evc, digits = 2)

#Eigenvector Centralization for Players with More than 10 Fights
cent_evc2 <- centr_eigen(deg_grt2_un)$centralization #Eigenvector Centralization of 0.91. Peripheral fighters mostly connect into the core and the core connects strongly to itself
round(cent_evc2, digits = 2)

#Eigenvector Centralization Whole Network
cent_all3 <- centr_eigen(un_net)$centralization
round(cent_all3, digits = 2)
```

Step 11. Cliques
```{r}
cliques(deg_no_iso) #cliques in the directed graph
cliques(deg_un_no_iso) #cliques in the undirected graph
cliques(deg_no_iso, min = 5) #cliques in the directed graph of at least size 3
cliques(un_net, min = 3) #cliques in the undirected graph of at least size 3

max_cliques(deg_no_iso, min = 7) # max cliques (can't be absorbed into larger clique) of at least size 3

igraph::clique_num(deg_no_iso) # size of largest clique
igraph::clique_num(deg_un_no_iso)
igraph::clique_num(deg_grt2)

```

Step 12. K-Cores
```{r}
#Evaluate the K-Cores of the No-Isolate Network
kcore1 <- igraph::coreness(deg_no_iso)
kcore1 #core of each node (at least k degree)
table(kcore1) 
core_nums <- coreness(deg_no_iso)
which(core_nums == max(core_nums))
V(deg_no_iso)$name[core_nums == max(core_nums)]

#K-Core for Experienced Fighters
kcore2 <- igraph::coreness(deg_grt2)
kcore2 
table(kcore2) 
core_nums2 <- coreness(deg_grt2)
which(core_nums2 == max(core_nums2))
V(deg_grt2)$name[core_nums2 == max(core_nums2)]

#K-Core for Just Winners Brings in One Additional Players
kcore_out2 <- igraph::coreness(deg_grt2, mode = "out")
kcore_out2 
table(kcore_out2) 
core_nums2_out <- coreness(deg_grt2, mode = "out")
which(core_nums2_out == max(core_nums2_out))
V(deg_grt2)$name[core_nums2_out == max(core_nums2_out)]


```


Step 13. Create Network SNA Object Directed
```{r}

#Impute NA's

nodes_imp <- nodes %>%
  mutate(weight = ifelse(is.na(weight), median(weight, na.rm=TRUE), weight))

nodes_imp_2 <- nodes_imp %>%
    mutate(height_inches = ifelse(is.na(height_inches), median(height_inches, na.rm=TRUE), height_inches))


anyNA(nodes_imp_2$weight)
anyNA(nodes_imp_2$height_inches)

net_sna <- igraph::graph_from_data_frame(edges, directed = F, nodes_imp_2)
edges$dup <- igraph::which_multiple(net_sna)
edges2 <- edges %>% filter(dup == FALSE) #Remove Duplicate Edges As Fighters Can Win Multiple Times Over Same Alter

#Mutate The DataFrame to Account for Interdivisional/Conference Relationships
edges2 <- edges2 %>%
  mutate(
    same_division = as.integer(ego_division == alter_division),
    same_conference = as.integer(ego_conference == alter_conference)
  )

edges2
net_sna_ergm <- network(edges2, matrix.type = "edgelist",
                   directed = T, vertex.attr = nodes_imp_2)

net_sna_un_ergm <- network(edges2, matrix.type = "edgelist",
                   directed = F, vertex.attr = nodes_imp_2)

network::is.directed(net_sna_un_ergm)
network::is.multiplex(net_sna_un_ergm)
network::has.loops(net_sna_un_ergm)
net_sna_ergm

```


Step. 14. Types of Dyads in Our Network

```{r}
#Triad Analysis on the Entire NHL Network Undirected Network
un_net_sna_dyads <- network(edges, matrix.type = "edgelist", directed = F, multiple = T, vertex.attr = nodes) 
un_net_sna_dyads # multiple = T because undirected graphs treat ties as mutual

sna::dyad.census(un_net_sna_dyads)
sna::triad.census(un_net_sna_dyads)

#sna::mutuality(un_net_sna_dyads)
#sna::reciprocity(un_net_sna_dyads)
#sna::which_mutual(un_net_sna_dyads)

#Triad Analysis on the Entire NHL Directed Network
net_sna_dyads <- network(edges, matrix.type = "edgelist", directed = T, multiple = T, vertex.attr = nodes)
net_sna_dyads
sna::dyad.census(net_sna_dyads)
sna::triad.census(net_sna_dyads)

#network.size(net_sna_dyads)
#network.size(un_net_sna_dyads)
```


Step 15. Calculate Transitivity
```{r}
#Local Transitivity of the Directed Entire NHL Network - Shows That For Most Players, They're Opponents Do Not Fight Eachother, but There Are Some Tiny Clustered Pockets
trans <- igraph::transitivity(net, type = "local", isolates = "zero") 
# can say that isolates are NaN or zero
summary(trans)

#Local Transitivity of the Undirected Entire NHL Network
trans_un <- igraph::transitivity(un_net, type = "local", isolates = "zero") 
# can say that isolates are NaN or zero
summary(trans_un)

#Global Transitivity of the Directed Entire NHL Network - If Player A Fought B and C, There is a 14.47% Chance Player B Fought Player C
trans_glob <- igraph::transitivity(net, type = "global")
trans_glob

#Global Transitivity of the Directed Entire NHL Network
trans_glob_un <- igraph::transitivity(un_net, type = "global")
trans_glob_un

#Global Transitivity of the Undirected Entire NHL Network
trans_glob_un2 <- igraph::transitivity(deg_grt2_un, type = "global")
trans_glob_un2

#Global Transitivity of the Undirected No Isolate Network
trans_glob_un3 <- igraph::transitivity(deg_un_no_iso, type = "global")
trans_glob_un3
```

Step 16. Calculating Constraint of the Network
```{r}

#No Isolates
igraph::constraint(deg_un_no_iso)
summary(igraph::constraint(deg_un_no_iso)) #The Mean of 0.4268 would show fighters are often embedded within clustered subgroups as a value close to 1 indicates the fighter's contacts are all heavily connected together and supported by median being high

#Players with More than 10 Fights
summary(igraph::constraint(deg_grt2_un))

#Entire Undirected Network
summary(igraph::constraint(un_net))#As We Filter For More Than 10 Fights, the Constraint Drops Showing That A Core Fighting Population Functions As A Bridge Across Otherwise Disconnected Fight Circles

```

Step 17. Calculating the Efficiency of the Network

```{r}
global_efficiency(un_net)


local_efficiency(net)

average_local_efficiency(un_net)

#For No Isolates
global_efficiency(deg_un_no_iso)
# Global efficiency is the average of the inverse distances between all pairs of nodes 
# 0 if pair isn't reachable 

local_efficiency(deg_no_iso)
# To calcuate local efficienty, remove node and compute the shortest paths between neighbors
# Take the average of the inverse of the shortest path distances.
# 0 if node has fewer than two ties or isn't reachable

average_local_efficiency(deg_un_no_iso)
# Average local efficiency is the mean of the local efficiencies

#For Fights Greater Than 10
global_efficiency(deg_grt2_un)
# Global efficiency is the average of the inverse distances between all pairs of nodes 
# 0 if pair isn't reachable 

local_efficiency(deg_grt2)
# To calcuate local efficienty, remove node and compute the shortest paths between neighbors
# Take the average of the inverse of the shortest path distances.
# 0 if node has fewer than two ties or isn't reachable

average_local_efficiency(deg_grt2_un)
# Average local efficiency is the mean of the local efficiencies

#These numbers are showing us that fighter-heavy core is highly integrated has short geodesic distance which means we have mostly preipheral noise with a diffusion-ready backbone 
```

Step 18. Calculate the Density
```{r}
#### density####
den <- igraph::edge_density(un_net) 
den_noiso <- igraph::edge_density(deg_un_no_iso)
den_grt2 <- igraph:: edge_density(deg_grt2_un)

den
den_noiso
den_grt2

#sna::gden(net_sna, mode = 'digraph') #digraph is directed graph, graph is undirected graph
```
Step 19. Test Transitivity of the Network Against Density with CUG 
```{r}
#Entire NHL Network
deg_sna_all <- asNetwork(net)
Cug_Edges_sna_all <- sna::cug.test(deg_sna_all, sna::gtrans, cmode="edges")
plot(Cug_Edges_sna_all)
Cug_Edges_sna_all$obs.stat #our network
summary(Cug_Edges_sna_all$rep.stat)

deg_sna_all_un <- asNetwork(un_net)
Cug_Edges_sna_all_un <- sna::cug.test(deg_sna_all_un, sna::gtrans, cmode="edges")
plot(Cug_Edges_sna_all_un)
Cug_Edges_sna_all_un$obs.stat #our network
summary(Cug_Edges_sna_all_un$rep.stat)



#No Isolates Network
deg_no_iso_sna <- asNetwork(deg_no_iso)
Cug_Edges_no_iso <- sna::cug.test(deg_no_iso_sna, sna::gtrans, cmode="edges")
plot(Cug_Edges_no_iso)
Cug_Edges_no_iso$obs.stat #our network
summary(Cug_Edges_no_iso$rep.stat)

#No Isolates Network
deg_un_no_iso_sna <- asNetwork(deg_un_no_iso)
Cug_Edges_un_no_iso <- sna::cug.test(deg_un_no_iso_sna, sna::gtrans, cmode="edges")
plot(Cug_Edges_un_no_iso)
Cug_Edges_un_no_iso$obs.stat #our network
summary(Cug_Edges_un_no_iso$rep.stat)


#Fights Greater Than Network
deg_grt2_sna <- asNetwork(deg_grt2)
Cug_Edges_grt2 <- sna::cug.test(deg_grt2_sna, sna::gtrans, cmode="edges")
plot(Cug_Edges_grt2)
Cug_Edges_grt2$obs.stat #our network
summary(Cug_Edges_grt2$rep.stat) # simulated networks

#Fights Greater Than Network
deg_grt2_sna_un <- asNetwork(deg_grt2_un)
Cug_Edges_grt2_un <- sna::cug.test(deg_grt2_sna_un, sna::gtrans, cmode="edges")
plot(Cug_Edges_grt2_un)
Cug_Edges_grt2_un$obs.stat #our network
summary(Cug_Edges_grt2_un$rep.stat) # simulated networks
# ours is higher than simulations
```

Step 20. Test Transitivity Against Dyad Cenus
```{r}
#No Isolates Network
Cug_Dyad_no_iso <- sna::cug.test(deg_no_iso_sna, sna::gtrans, cmode="dyad.census")
plot(Cug_Dyad_no_iso)
Cug_Dyad_no_iso$obs.stat #our network
summary(Cug_Dyad_no_iso$rep.stat) # simulated networks
# ours is higher than simulations
```

Step 21. Test Transitivity Against Size
```{r}
# Test Transitivity against the size####
Cug_size_no_iso <- sna::cug.test(deg_no_iso_sna, sna::gtrans, cmode="size")
plot(Cug_size_no_iso)
Cug_size_no_iso$obs.stat #our network
summary(Cug_size_no_iso$rep.stat) # simulated networks
# ours is lower than simulations

```


Step 22. Basic ERGM Model
```{r}
model1 <- ergm(net_sna_un_ergm ~ edges)
summary(model1) #This is telling me that there is a 0.52% chance that any two NHL players fought over the last 25 years
mod_sum <- summary(model1) 
beta <- coef(mod_sum)[1]
beta <- mod_sum$coefficients[1] 
beta 

prob <- exp(beta)/(1+exp(beta)) 
prob # the probability of forming a tie with someone else at random is 0.52%
sna::gden(net_sna_un_ergm) 

#Naturally, The Probability of Winning a Fight Over Another Player is Half of That of Engaging at 0.26%
model2 <- ergm(net_sna_ergm ~ edges)
summary(model2) #This is telling me that there is a 0.26% chance that any NHL player can claim victory in a fight over any other player in the NHL
mod_sum2 <- summary(model2)
mod_sum2
beta2 <- coef(mod_sum)[1]

prob2 <- exp(beta2)/(1+exp(beta2)) 
prob2 
sna::gden(net_sna_ergm) 

```

Step 23. Finding Communities with Leading EigenVector 
```{r}
#All NHL Fighters
cle_sna_un_ergm <- intergraph::asIgraph(net_sna_un_ergm)
set.seed(1)
cle <- cluster_leading_eigen(cle_sna_un_ergm) #for undirected graphs
modularity(cle) 
membership(cle) 
length(cle)
sizes(cle)

colors <- colorpanel(length(cle), low = "#efd9d3", high = "#57424a")
ggraph(deg_un_no_iso) + 
  geom_edge_link0(color = "black", alpha = .5) +
  geom_node_point(aes(fill = as.factor(membership(cle))),
                  size = sqrt(igraph::degree(deg_un_no_iso, mode = "all")), 
                  color = "black", shape = 21) +
  scale_fill_manual(values = c(colors)) +
  ggnetwork::theme_blank() +
  theme(legend.position = "none")

#For Players with More Than 10 Fights
set.seed(1)
cle_grt2 <- cluster_leading_eigen(deg_grt2_un) #for undirected graphs
modularity(cle_grt2) 
membership(cle_grt2) 
length(cle_grt2)
sizes(cle_grt2)

colors <- colorpanel(length(cle_grt2), low = "#efd9d3", high = "#57424a")
ggraph(deg_grt2_un) + 
  geom_edge_link0(color = "black", alpha = .5) +
  geom_node_point(aes(fill = as.factor(membership(cle_grt2))),
                  size = sqrt(igraph::degree(deg_grt2_un, mode = "all")), 
                  color = "black", shape = 21) +
  scale_fill_manual(values = c(colors),
                    name = "Community",
                    guide = guide_legend(override.aes = list(size = 4))) +
  ggnetwork::theme_blank() +
  theme(legend.position = "bottom")

```

Step 24. Finding Communities with SpinGlass
```{r}
#For Fighters with More Than 10 Fights
set.seed(1)
csg <- cluster_spinglass(deg_grt2_un)
modularity(csg) 
membership(csg) 
length(csg)
sizes(csg)

colors <- colorpanel(length(csg), low = "#efd9d3", high = "#57424a")
ggraph(deg_grt2_un) + 
  geom_edge_link0(color = "black", alpha = .5) +
  geom_node_point(aes(fill = as.factor(membership(csg))),
                  size = sqrt(igraph::degree(deg_grt2_un, mode = "all")), 
                  color = "black", shape = 21) +
  scale_fill_manual(values = c(colors),
                    name = "Community",
                    guide = guide_legend(override.aes = list(size = 4))) +
  ggnetwork::theme_blank() +
  theme(legend.position = "bottom")

```

Step 25. Adding terms to the ERGM Model
```{r}

#Model 3 Currently Does Not Work Due to Handendness Having N/A Values - Probably not Worth the Time
#model3 <- ergm(net_sna_ergm ~ edges + 
                 #nodecov("height_inches") +
                 #nodecov("weight") +
                #nodefactor("position")) 
#summary(model3)


#Model 4 Shows No Sigfnificant Coorelation Between Out of Fights and Height
model4 <- ergm(net_sna_ergm ~ edges + 
                 nodecov("height_inches"))
summary(model4)
plogis(coef(model4))
 
#Model 5 Shows No Significant Correlation Betweeen Amount of Fights and Weight
model5 <- ergm(net_sna_ergm ~ edges + 
                 nodecov("weight"))
summary(model5) 


#Model 6 Shows A Significant Coorelation Bewtween Both Height and Weight and the Number of Fights a Player Has
model6 <- ergm(net_sna_ergm ~ edges + 
                 nodecov("weight")+
                 nodecov("height_inches"))
summary(model6)
plogis(coef(model6))
mod_sum6 <- summary(model6)

model7 <- ergm(net_sna_ergm ~ edges + 
                 nodeicov("weight") +
                 nodeocov("weight"))
summary(model7) 

model7 <- ergm(net_sna_ergm ~ edges + 
                 nodeicov("height_inches") +
                 nodeocov("height_inches"))
summary(model7)

model8 <- ergm(net_sna_ergm ~ edges + 
                 nodeicov("height_inches") +
                 nodeocov("height_inches") +
                 nodeicov("weight") +
                 nodeocov("weight"))
summary(model8)


network::list.edge.attributes(net_sna_ergm)

```

Step 26. TERGM
```{r}
#Get the Unique Players in Each Season to How Many Players Are Fighting
seasons <- sort(unique(edges2$missing_season))

nets_by_season_un <- lapply(seasons, function(s) {
  df <- edges2[edges2$missing_season == s, c("ego_id","alter_id")]
  network(df, directed = FALSE, matrix.type = "edgelist")
})


nets_by_season <- lapply(seasons, function(s) {
  df <- edges2[edges2$missing_season == s, c("ego_id","alter_id")]
  network(df, directed = TRUE, matrix.type = "edgelist")
})

names(nets_by_season) <- seasons
class(net_sna_ergm)
is.network(net_sna_ergm)



net_dyn <- networkDynamic(network.list = nets_by_season, vertex.pid = "vertex.names") # make a dynamic network object
net_dyn_un <- networkDynamic(network.list = nets_by_season_un, vertex.pid = "vertex.names") # make a dynamic network object

net_dyn
net_dyn_un1

library(tsna)
# tSnaStats
tSnaStats(net_dyn,"degree") 

# tErgmStats gets regular ergm term statistics across time
tErgmStats(net_dyn, "~ edges+mutual")
tErgmStats(net_dyn_un, "~ edges")

## edgeDuration gets the amount of time edges are active. 
# subject = "edge" is aggregated across all activities in which that edge is involved. 
table(edgeDuration(net_dyn, mode = "duration", subject = "edge")) # it's a table of edge occuraces
table(edgeDuration(net_dyn_un, mode = "duration", subject = "edge"))

# subject = "spell" is a single interval when an edge is active. An edge can have multiple spells. 
table(edgeDuration(net_dyn, mode = "duration", subject = "spells")) # it's a table of edge durations
table(edgeDuration(net_dyn_un, mode = "duration", subject = "spells"))


## vertexDuration gets the amount of times nodes are active. 
table(vertexDuration(net_dyn, mode = "duration", subject = "vertices")) 
table(vertexDuration(net_dyn, mode = "duration", subject = "spells")) 


table(vertexDuration(net_dyn_un, mode = "duration", subject = "vertices")) 
table(vertexDuration(net_dyn_un, mode = "duration", subject = "spells")) 

fit_tergm <- tergm(
  net_dyn ~
    Form(~ edges + mutual),
  estimate = "CMLE",
  times = 1:4
)
summary(fit_tergm)

```


Step 27. Fit the TERGM Model
```{r}
#### Form() + Persist()
fit_tergm <- tergm(
  net_dyn_un ~
    Form(~ edges),
  estimate = "CMLE",
  times = 0:25
)
summary(fit_tergm)

fit_stergm <- tergm(
  net_dyn_un ~ Form(~ edges) + Persist(~ edges),
  estimate = "CMLE",
  times = 0:25,
)
summary(fit_stergm)
```

Step 28. Evaluating Goodness of Fit of the ERGM Models
```{r}
#It is the Same Underlying Network Since Isolates are Not Accounted For so Same Plots
gof.model6_btergm <- btergm::gof(model6, nsim = 100, 
                                 statistics = c(esp, deg, odeg, ideg, geodesic, fastgreedy.modularity))
gof.model6_btergm
plot(gof.model6_btergm)

gof.model8_btergm <- btergm::gof(model8, nsim = 100, 
                                 statistics = c(esp, deg, odeg, ideg, geodesic, fastgreedy.modularity))
gof.model8_btergm
plot(gof.model8_btergm)
```



Step 29. Diffusion in the Network
```{r}
#Did not Find this Super Useful for My Experimentation
net_sna_adj_un <- as_adjacency_matrix(un_net)
n_nodes <- nrow(net_sna_adj_un)
n_nodes

set.seed(1)
diffnet_il <- rdiffnet(
  t = 26, 
  seed.graph = net_sna_adj_un,
  # rgraph.args = list(p = 0.3), #don't need because we're using a real graph
  seed.nodes = c(170, 56, 271), # chosen nodes
  seed.p.adopt = 1,
  rewire = F,
  threshold.dist = function(i) 0.02, 
  exposure.args = list(normalized = T)
  )
diffnet_il
summary(diffnet_il)
table(diffnet_il$toa) # time of adoption
plot_diffnet(diffnet_il, slices = c(170, 56, 271))
plot_adopters(diffnet_il, what = "adopt")
plot_adopters(diffnet_il, what = "cumadopt", include.legend = FALSE)

toa <- diffnet_il$toa  # pull time of adoption
adopted_at_time_1 <- !is.na(toa) & toa <= 1  
il_nets <- diffnet_to_igraph(diffnet_il, slices=c(1:10))
il_net_t1 <- il_nets[[1]]  
V(il_net_t1)$adopted <- adopted_at_time_1  
il_net_plot <- ggraph(il_net_t1) + 
  geom_edge_link(alpha = 0.5) +
  geom_node_point(aes(color = adopted), size = 3) +
  scale_color_manual(values = c("black", "red")) +
  theme_graph()
il_net_plot

diffnet_sw <- rdiffnet(
  n = 4572, #4572 nodes
  t = 26, # 26 time points
  seed.graph = "small-world", #small-world graph
  rgraph.args = list(p = 0.00107), #0.1% tie probability
  seed.nodes = c(170, 56, 271), # chosen nodes
  seed.p.adopt = 0.1, #10% early adopters
  rewire = F, #rewire the network
  threshold.dist = function(i) 0.25, # % alters that need to adopt before ego will
  exposure.args = list(normalized = T) 
)
diffnet_sw

summary(diffnet_sw) 

table(diffnet_sw$toa) # time of adoption
plot_diffnet(diffnet_sw, slices = c(170, 56, 271))
plot_adopters(diffnet_sw, what = "adopt")
plot_adopters(diffnet_sw, what = "cumadopt", include.legend = FALSE)

```